Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-06 prop_letter.tex
prop_letter.tex Here and there...

Quantum IVPMs provide a unifying framework to account for 
finite precision measurements in quantum physics. It has the desired 
properties of turning into the classical IVPMs setup~\cite{JamisonLodwick2004}
when the space of events includes only mutually commuting sub-events, and 
of leading to the standard von Neumann projective measurement theory when 
the collection of intervals are all singletons. To be more precise....

Although considering IVPM is new for a quantum theory, people have
already defined classical IVPMs~\cite{JamisonLodwick2004}, which
are essentially the same as quantum IVPMs on a restricted mutually
commuting sub-event space~$\events'\subseteq\events$, where any
subset of $\events$ is called a sub-event space if it satisfies the
follow conditions.
\begin{itemize}
\item $\mathbb{0}\in\events'$.
\item $\mathbb{1}\in\events'$.
\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$.
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$.
\end{itemize}
Quantum IVPM not only stems from classical IVPM but also generalizes
quantum real-valued probability measures which can be expressed a
limiting case when the collection of intervals are 
all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
where Gleason's theorem is applied. However, it certainly contains
richer phenomena. For example, we will show the 
Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
is another limiting case when the collection of intervals are 
$\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
in the next paragraph.

@@

>>>>

Quantum IVPMs provide a unifying framework to account for finite precision
measurements in quantum physics. It has the desired properties of
turning into the classical IVPMs setup~\cite{JamisonLodwick2004}
when the space of events includes only mutually commuting sub-events,
and of leading to the standard von Neumann projective measurement
theory when the collection of intervals are all singletons. To be
more precise....\newpage{}

Although considering IVPM is new for a quantum theory, people have
already defined classical IVPMs~\cite{JamisonLodwick2004}, which
are essentially the same as quantum IVPMs on a restricted mutually
commuting sub-event space~$\events'\subseteq\events$, where any
subset of $\events$ is called a sub-event space if it satisfies the
follow conditions. 
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection $P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
Quantum IVPM not only stems from classical IVPM but also generalizes
quantum real-valued probability measures. Consider the collection
of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
and a function~$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
defined by $\iota_{\infty}\left(x\right)=\left[x,x\right]$. Then,
given a quantum real value probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM, and vice
versa. In another word, when quantum IVPMs with $\mathscr{I}_{\infty}$
are just the same as quantum real-valued probability measures which
can fit Gleason's theorem.

However, quantum IVPMs certainly contains richer phenomena. For example,
we will show the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
is another limiting case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
in the next paragraph.

@@

Recall when providing infinity measurement resource, the quantum probability
measures are simply induced by the Born rule for $d\ge3$. If we increase
the measurement resource, i.e., pick finer intervals when constructing
IVPMs, it would be natural to ask whether quantum IVPMs would approach
the Born rule. In order to understand this question, it is instructive
to consider the 2-dimensional non-Born quantum probability measure~$\mu:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu(P)=\begin{cases}
\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P=\proj{\ps}\textrm{ or }\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
\end{cases}
\end{equation}
Notice that $\mu$ is consistent with the Born rule partially, because
it is computed according to different states when applying on different
projectors. \newpage{}
